Conversations in time: interactive visualisation to explore structured temporal data

### 2020-08-18 tsibbletalk.Rmd
sections reorganised

# Related works: interactive visualisation systems with linking views

* {ggobi} and {xggobi}
* {cranvas} and {cranvastime}
* [crossfilter.js](http://crossfilter.github.io/crossfilter/) & [dc.js](https://dc-js.github.io/dc.js/)
* {crosstalk} and html widgets

# Motivation: tidy temporal data and workflow

@@

In the spirit of tidy data to the \CRANpkg{tidyverse} [@Wickham2019], the **tidyverts** suite features `tsibble` as the foundational data structure, in order to build a fluid and fluent pipeline for time series analysis. Besides \CRANpkg{tsibble}, the \CRANpkg{feasts} and \CRANpkg{fable} packages fill the role of statistical analysis and forecasting in the **tidyverts** ecosystem. When time series analysis starts taking off, series of interest denoted by the `key` variables often remain unchanged over the course of analysis, from trend inspection to forecasting performance. Figure \ref{fig:highlight-retail} (a) gives an overview of 152 series for the retail data using an overlaid time series plot, while Figure \ref{fig:highlight-retail} (b) presents a scatterplot, where each series is represented by a dot in the feature space (trend versus seasonal strength). The plot making of Figure \ref{fig:highlight-retail} (b) is aided with the `features()` function from \CRANpkg{feasts}, which summarises original data by each series down to various statistical features. This function along with other **tidyverts** functions is `tsibble`-aware, and outputs a table in a reduced form where each row corresponds to a series, thus graphically displayed as Figure \ref{fig:highlight-retail} (b).

@@

# Shared temporal data for coordinated views with examples

@@

# Slicing and dicing time with examples

>>>>

# Background: tidy temporal data and workflow

@@

In the spirit of tidy data to the \CRANpkg{tidyverse} [@Wickham2019], the **tidyverts** suite features `tsibble` as the foundational data structure, in order to build a fluid and fluent pipeline for time series analysis. Besides \CRANpkg{tsibble}, the \CRANpkg{feasts} and \CRANpkg{fable} packages fill the role of statistical analysis and forecasting in the **tidyverts** ecosystem. When time series analysis starts taking off, series of interest denoted by the `key` variables often remain unchanged over the course of analysis, from trend inspection to forecasting performance.

Figure \ref{fig:highlight-retail} (a) gives an overview of 152 series for the retail data using an overlaid time series plot, while Figure \ref{fig:highlight-retail} (b) presents a scatterplot, where each series is represented by a dot in the feature space (trend versus seasonal strength). The plot making of Figure \ref{fig:highlight-retail} (b) is aided with the `features()` function from \CRANpkg{feasts}, which summarises original data by each series down to various statistical features. This function along with other **tidyverts** functions is `tsibble`-aware, and outputs a table in a reduced form where each row corresponds to a series, thus graphically displayed as Figure \ref{fig:highlight-retail} (b).

@@

# Overview of interactivity

* {cranvas} and {cranvastime}
* [crossfilter.js](http://crossfilter.github.io/crossfilter/) & [dc.js](https://dc-js.github.io/dc.js/)
* {crosstalk} and html widgets
* {rJava}, {rbokeh} {loon}

# Interactivity for coordinated views via shared temporal data

@@

# Slicing and dicing time

### 2020-08-18 tsibbletalk.tex
sections reorganised

\hypertarget{related-works-interactive-visualisation-systems-with-linking-views}{%
\section{Related works: interactive visualisation systems with linking
views}\label{related-works-interactive-visualisation-systems-with-linking-views}}

\begin{itemize}
\tightlist
\item
  \{ggobi\} and \{xggobi\}
\item
  \{cranvas\} and \{cranvastime\}
\item
  \href{http://crossfilter.github.io/crossfilter/}{crossfilter.js} \&
  \href{https://dc-js.github.io/dc.js/}{dc.js}
\item
  \{crosstalk\} and html widgets
\end{itemize}

\hypertarget{motivation-tidy-temporal-data-and-workflow}{%
\section{Motivation: tidy temporal data and
workflow}\label{motivation-tidy-temporal-data-and-workflow}}

@@

\hypertarget{shared-temporal-data-for-coordinated-views-with-examples}{%
\section{Shared temporal data for coordinated views with
examples}\label{shared-temporal-data-for-coordinated-views-with-examples}}

@@

\hypertarget{slicing-and-dicing-time-with-examples}{%
\section{Slicing and dicing time with
examples}\label{slicing-and-dicing-time-with-examples}}

>>>>

\hypertarget{background-tidy-temporal-data-and-workflow}{%
\section{Background: tidy temporal data and
workflow}\label{background-tidy-temporal-data-and-workflow}}

@@

\hypertarget{overview-of-interactivity}{%
\section{Overview of interactivity}\label{overview-of-interactivity}}

\begin{itemize}
\tightlist
\item
  \{cranvas\} and \{cranvastime\}
\item
  \href{http://crossfilter.github.io/crossfilter/}{crossfilter.js} \&
  \href{https://dc-js.github.io/dc.js/}{dc.js}
\item
  \{crosstalk\} and html widgets
\item
  \{rJava\}, \{rbokeh\} \{loon\}
\end{itemize}

\hypertarget{interactivity-for-coordinated-views-via-shared-temporal-data}{%
\section{Interactivity for coordinated views via shared temporal
data}\label{interactivity-for-coordinated-views-via-shared-temporal-data}}

@@

\hypertarget{slicing-and-dicing-time}{%
\section{Slicing and dicing time}\label{slicing-and-dicing-time}}
